Constant-round Blind Classical Verification of Quantum Sampling

### 2020-09-10 introduction.tex
Fix wording

\Ethan{This paragraph is new and has to be checked}
Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
it is still unclear how to construct a CVQC protocol for $\SampBQP$.
A protocol for classical sampling problems is usually obtained from one for decision problems,
by fixing a seed for pseudorandomness then computing the output bit-by-bit.
This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements,
where the outcome is generally different from one execution to the next.
Furthermore, it is unclear how to even amplify the soundness of a sampling protocol by means of repetitions,
especially considering the outputs from different executions might be correlated to begin with.

>>>>

\Ethan{This paragraph is new and has to be checked}
Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
it is still unclear how to construct a CVQC protocol for $\SampBQP$.
A protocol for classical sampling problems is usually obtained from that of decision problems,
by fixing a seed for pseudorandomness then computing the output bit-by-bit.
This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements,
where the outcome is generally different from one execution to the next.
Furthermore, it is unclear how to even amplify the soundness of a sampling protocol by means of repetitions,
especially considering the outputs from different executions might be correlated to begin with.
